Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-08 ms.tex
removed some outdated outline items

\section{Systematics}

\subsection{CIBA}
Perhaps the dominant limitation of our fits is the presence of cosmic
infrared background anisotropies (CIBA) bleeding through into our maps of 
Galactic dust temperature and optical depth in high-latitude regions 
\citep{ciba}.
\subsubsection{Simulations}

\subsubsection{Optimizing Relative Weights}

%not sure if below subsection is necessary, idea of giving zero weight to 217 
%GHz may belong in above subsection

%\subsubsection{Omitting 217 GHz}
%The \cite{planckdust} result used only 353, 545, 857, and 3000 GHz. When we 
%repeat our analysis ignoring 217 GHz, so that we are using the same
%set of frequencies, we find that no major changes arise. This actually
%should be done/investigated though.

\subsection{Zero Point}
Simulate the effect of getting zero points wrong to quantiy this
systematic a bit.

\subsection{$T_{2}$ Prior}
Use FIRAS data to justify $T_2$ prior. Could I use the DIRBE 100/240 micron
ratio to get a $1.3^{\circ}$ resolution prior on $T_2$?

\subsection{Other Limitations}
\IRAS~is missing in some parts of sky which will therefore not truly have 6.1' 
resolution.
%any other miscellaneous issues?

@@

%\subsection{Calculating $\tau$}

% this subsection should probably be moved to the ``dust emission model'' 
% section of the paper eventually

@@

\subsection{Data Release}
We are releasing nside=2048 HEALPix maps in Galactic coordinates summarizing 
the results of of our two-component dust fits.

>>>>

%%\section{Systematics}
%%
%%\subsection{CIBA}
%%Perhaps the dominant limitation of our fits is the presence of cosmic
%%infrared background anisotropies (CIBA) bleeding through into our maps of 
%%Galactic dust temperature and optical depth in high-latitude regions 
%%\citep{ciba}.
%%\subsubsection{Simulations}

%%\subsubsection{Optimizing Relative Weights}

%%\subsection{Zero Point}
%%Simulate the effect of getting zero points wrong to quantiy this
%%systematic a bit.

%%\subsection{$T_{2}$ Prior}
%%Use FIRAS data to justify $T_2$ prior. Could I use the DIRBE 100/240 micron
%%ratio to get a $1.3^{\circ}$ resolution prior on $T_2$?

%%\subsection{Other Limitations}
%%\IRAS~is missing in some parts of sky which will therefore not truly have 
%%6.1' resolution.
%%any other miscellaneous issues?

@@

\subsection{Data Release}
We are releasing $N_{side}$=2048 HEALPix maps in Galactic coordinates 
summarizing the results of of our two-component dust fits.

@@
